---
title: "Survey Data Quality and Weighting Report"
author: "Feng Luan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview

This report summarizes a reproducible survey data quality and weighting workflow using simulated respondent-level survey data.

```{r load-data}
quality_summary <- read.csv("../output/quality_control_summary.csv")
weighted_estimates <- read.csv("../output/weighted_estimates.csv")
weight_summary <- read.csv("../output/weight_summary.csv")
weighting_diagnostics <- read.csv("../output/weighting_diagnostics.csv")
```

## Quality Control Summary

```{r quality-summary}
quality_summary
```

## Weight Summary

```{r weight-summary}
weight_summary
```

## Raking Diagnostics

```{r raking-diagnostics}
tail(weighting_diagnostics, 10)
```

## Weighted and Unweighted Estimates

```{r weighted-estimates}
weighted_estimates
```

## Interpretation

The workflow first identifies potentially low-quality responses using respondent-level quality flags. After excluding respondents with multiple quality concerns, the cleaned survey sample is weighted using raking so that the sample better aligns with external benchmark distributions.

The final output compares unweighted and weighted estimates for each survey item.
